---
title: "Cabbages"
author: "Ashley Saunders"
date: "9/3/24"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(VitC~Cult,data=veggy)
```

Based on the graphical results shown from this boxplot, we can conclude that Cult 52 has a significantly higher amount of Vitamin C that Cult 39, with c39 having an IQR of around 45 to 55 VitC, while c52 has an IQR of around 58 to 70 VitC.

## Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```
The Numerical result patterns show a notable difference between Cult 39 and Cult 52. Cult 39 has a lower mean with it being at 51.5, while Cult 52 has a higher mean, it being at 64.4. This is the same with the median. C39 has a lower median at 51.0, while c52 has a higher median at 64.5. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(VitC~Cult,data=veggy)
```
The hypothesis we can conclude is that the p-value of Vitamin C by Cult is 3.405e-08, t = -6.3909, and df = 56.376, with a 95 percent confidence interval. The t-test satisfys the assumptions and is appropriate for this procedure because it efficiently determines the correlation coefficient, so with this test, we can conclude that the assumptions are correct because we can see that the mean is significantly lower for c39 at 51.5 while c52 has a mean much higher at 64.4.  

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
Throughout this assignment, we utilized the T-test and Boxplot in order to determine Vitamin C levels for Cult 39 and Cult 52. With these procedures, we conclude that Cult 39 has a significantly lower amount of Vitamion C than Cult 52. We can come to this conclusion because the evidence from our procedures clearly state that C39 has a mean of 51.5 which is lower than the mean of C52, being at 64.4. C39 also has a max of 68 while C 52 has a max of 84, which is significantly higher.